\vspace{-2cm} Government websites as data: A methodological pipeline for collection, processing, and text analysis

### 2018-05-09 paper/manuscript.tex
added background on the significance of gov website use

>>>>

Some papers on how government websites are used
\begin{itemize}
\item \cite{sandoval2012government}, p.S74, ``Usually citizens access government websites to find information and
data for decision making''.
\item In a survey conducted among a random sample of citizens in the state of Georgia in 2000, \cite{thomas2003new} found that nearly 25\% of internet users in the sample reported visiting a local government website in the previous twelve months to gather information. We would expect that number to be even larger nearly two decades later.
\item \cite{tolbert2006effects} p. 355, ``We ?nd that users of local government Web sites are more likely to trust local governments, controlling for other demo-graphic factors, and that the use of government Web sites is associated with other positive attitudes, espe-cially for federal and local governments. ''
\end{itemize}
